On the analytic structure of the linear response susceptibility in open systems

### 2018-03-14 AnalyticStructure_main.tex
update

% The knowledge of the long range behavior of the fluctuation states allows us to perform an assessment on the reliability of the evaluation of the linear response functional 
% \eqref{LinearResponseFunctDef1}. To elaborate this statement we make usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, 
% so that:
% The knowledge of the long range behavior of the fluctuation states allows us to assess the spatial localization properties of the basic objects relevant in the contest of the 
% linear response. In particular, making usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear 
% response functional \eqref{LinearResponseFunctDef1} as follows: 
This analysis allows us to comprehend that the spatial localization features of the building blocks relevant for the linear response depend critically on $\omega$. 
Indeed, the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1} implies that
\be\lb{LinearResponseFunctDef2}
\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
\ee
so we can identify two different regimes, depending on the value of $\omega$. In the first one, realized for $\omega<|\eps_h|$, all the terms contributing to \eqref{LinearResponseFunctDef2} 
are expressed in terms of genuinely localized wave functions, while in the second one, for $\omega>|\eps_h|$, fluctuation states start behaving as unbound wave functions. 
%and the scalar products appearing in \eqref{LinearResponseFunctDef2} are only regularized by the long range behavior of the $\ket{\psi_p}$.
This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
to the value of $\omega$. 
This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....

>>>>

% The knowledge of the long range behavior of the fluctuation states allows us to perform an assessment on the reliability of the evaluation of the linear response functional 
% \eqref{LinearResponseFunctDef1}. To elaborate this statement we make usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, 
% so that:
% The knowledge of the long range behavior of the fluctuation states allows us to assess the spatial localization properties of the basic objects relevant in the contest of the 
% linear response. In particular, making usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear 
% response functional \eqref{LinearResponseFunctDef1} as follows: 
% This analysis indicates that the task of providing a reliable assessment of the linear response functional present a different level of complexity   .
% Using the representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear response functional as
% \be\lb{LinearResponseFunctDef2}
% \braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
% \ee
This analysis allows us to determine the spatial localization features of the building blocks\footnote{This consideration holds for the class of observables that produces a localized state 
$\bra{\psi_p}\op O$ when acts on a bound eigenstate of $\hnot$} relevant for the linear response.  
%and provides indications on the da alcune indicazioni sulla difficoltà di ottenere una reliable evaluation of the linear response functional. %change in function of $\omega$. 
Indeed, using the fluctuation states representation of the response density, we can express the linear response functional \eqref{LinearResponseFunctDef1} as
%Indeed, the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1} implies that
\be\lb{LinearResponseFunctDef2}
\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
\ee
An inspection of \eqref{LinearResponseFunctDef2} evidences that we can identify two different regimes, depending on the value of $\omega$. In the first regime, realized for $\omega<|\eps_h|$, 
the linear response is formulated in terms of genuinely quantities, each of which possess a physical cut-off radius. In this case it is possible to evaluate of the scalar products of 
\eqref{LinearResponseFunctDef2} using a finite computational domain and the long range behavior of both $\{\ket{f_p(\omega)}\}$ and $\{\bra{\psi_p}\op O\}$ ensures that the result is not 
affected by the specific choice of the domain. This is an argument in favor of the reliable evaluation of the linear response functional in the low-$\omega$ regime.    
%is reasonable to expect that the result of () should be independent
%from the computation domain used to evaluate the scalar products,  choosing a finite computational
%domain to perform the scalar products of \eqref{LinearResponseFunctDef2} does not affect the result, provided that the degrees of freedom included are able to contain the waist of the elements
%considered.

scegliendo un dominio computazionale
finito per eseguire i prodotti scalari espressi nella \eqref{LinearResponseFunctDef2}, i risultati ottenuti siano indipendenti dalla particolare scelta eseguita a patto che i gradi di libertà
utilizzati permettano di contenere la taglia degli oggetti considerati.

sia possibile ottenere una valutazione
affidabile della risposta lineare eseguendo i prodotti scalari espressi nella \eqref{LinearResponseFunctDef2}  in un dominio computazione finito in grado di contenere i building blocks a reliable evaluation
of \eqref{LinearResponseFunctDef2} can be provided if the building elements are computed in a finite domain which contains the cut.off

\vspace{1cm}
are expressed in terms of genuinely localized wave functions, while in the second one, for $\omega>|\eps_h|$, fluctuation states start behaving as unbound wave functions. 
%and the scalar products appearing in \eqref{LinearResponseFunctDef2} are only regularized by the long range behavior of the $\ket{\psi_p}$.
This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
to the value of $\omega$. 
This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....
